How to Avoid OOTA Without Really Trying

### 2024-10-12 paper/ootavacuous.tex
ootavacuous: Section 8 s/One/The/
Suggested-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

One conclusion to be drawn from this work is that in this context,
avoiding OOTA cycles requires no changes to the standard,
to current implementions, or to user practices for portable code.
% This work also demonstrates the need for caution when optimizing
% atomic operations.

>>>>

The conclusion to be drawn from this work is that in this context,
avoiding OOTA cycles requires no changes to the standard,
to current implementions, or to user practices for portable code.
% This work also demonstrates the need for caution when optimizing
% atomic operations.
